### 2025-08-26 getting-started.qmd
20250826 - updated instructions

To get started, follow the following steps:

1. Install `R`: <https://cran.r-project.org>
1. Install `RStudio Desktop`: <https://posit.co/download/rstudio-desktop>
1. After installing `RStudio`, open `RStudio` and run the following code in the console to install the `R` packages used in this book (note: this will take a while):
   ```{r}
   #| eval: false

>>>>

To get started, follow the following steps (for each step that involves installing or running software, make sure to right click and select "Run as Administrator"):

1. Download and install `R`: <https://cran.r-project.org>
1. After installing `R`, download and install `RStudio Desktop`—this is a graphical user interface for `R`: <https://posit.co/download/rstudio-desktop>
1. Install tools to allow you to compile `R` packages so you can install packages from source, if necessary (i.e., if package binaries are not available):
    - If on Windows, download and install the version of `RTools` (<https://cran.r-project.org/bin/windows/Rtools/>) that corresponds to your version of `R`
    - If on Mac, download and install `R Compiler Tools for Rcpp on MacOS`: <https://thecoatlessprofessor.com/programming/cpp/r-compiler-tools-for-rcpp-on-macos/>
1. After installing `R` and `RStudio`, open `RStudio` (by right clicking and selecting "Run as Administrator") and run the following code in the console to install the `R` packages used in this book (note: this will take a while):
   ```{r}
   #| eval: false
